\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\microtypesetup{protrusion=false,expansion=false}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.9]{geometry}
\usepackage{xcolor}
\setlength{\footskip}{30pt}

\name{}{Benjamin Desprets}
% \title{Full-Stack Developer}
\born{11/10/2003}
% \address{Paris, France}
\phone[mobile]{+33~(0)~6~28~74~90~94}
\email{benjamin@desprets.net}
\homepage{desprets.net}
\social[github]{bendrsio}
\social[linkedin]{benjamindesprets}

\begin{document}
\makecvtitle

Results-driven 4th-year software engineering student at Epitech with full-stack, automation and blockchain experience. 
A fast learner and passionate team player, keen to build innovative solutions. Bi-lingual (English, French) with excellent communication and interpersonal skills.

\section{Experience}
\cventry{Sep 2024--Apr 2025}{Web and Onchain Developer}{ETH Investors Club}{Remote}{}{
  \begin{itemize}
    \item Deployed and maintained an onchain article minting system generating \$150k+ revenue.
    \item Developed and updated the \href{https://ethinvestorsclub.com}{ethinvestorsclub.com} website.
  \end{itemize}
}
\cventry{Feb 2024--Aug 2024}{Robotic Process Automation Software Developer}{EssilorLuxottica}{Créteil, FR}{}{
  \begin{itemize}
    \item Led internal automation projects, simplifying processes and boosting efficiency.
  \end{itemize}
}
\cventry{Jul 2022--Dec 2022}{Back End Developer}{}{}{}{
  \begin{itemize}
    \item Built and deployed internal billing app/service; managed database deployment and operational flows.
  \end{itemize}
}

\section{Education}
\cventry{2020--2026}{Master's in Software Engineering - International Track}{Epitech}{Berlin, DE / Montreal, CA / Paris, FR}{}{
  \begin{itemize}
    \item Delivered 50+ diverse projects alone or in groups of up to 6.
    \item Organised and led AI and Web3 development workshops for 30 students.
    \item Mastered advanced software engineering, full-stack development, and production system architecture.
   \end{itemize}
}
\cventry{2024--2025}{Certificate in Management}{McGill University}{Montreal, CA}{}{
  \begin{itemize}
    \item GPA: 3.5 — focus on finance, mathematics, and strategic management.
    \item Developed practical business skills through real-world case studies, data-driven analysis, and team-based projects.
  \end{itemize}
}

\section{Projects}
\cventry{}{The easiest wallet in the world!}{\href{https://fundamentalwallet.com}{Fundamental}}{}{}{
  \begin{itemize}
    \item Founded and led a team of 5 to develop a user-friendly, mobile-first crypto wallet.
    \item Designed the app and wallet architectures, perfected UI/UX and deployed a custom ENS registry.
  \end{itemize}
}
\cventry{}{Text-based AI image editor}{\href{https://imagn.xyz}{imagn.xyz}}{}{}{
  \begin{itemize}
    \item Engineered AI SaaS for natural language image editing.
    \item Prioritized UX, image quality and cutting-edge AI (Gemini 2.0 Flash).
  \end{itemize}
}
\cventry{}{Personal Website \& Interactive CV}{\href{https://desprets.net}{desprets.net}}{}{}{
  \begin{itemize}
    \item Developed an interactive résumé and project showcase with a Markdown-based CMS for detailed write-ups and easy updates.
  \end{itemize}
}

% \section{Achievements}
% \cvitem{}{Top 20\% in LeetCode contests, showcasing strong algorithmic \& programming skills.}

\section{Skills}
\cvitem{Languages}{TypeScript, JavaScript, Python, C++, C, Lua}
\cvitem{Frontend}{React, React Native, Next.js, HTML, Tailwind}
\cvitem{Backend}{Node.js, SQL, REST APIs}
\cvitem{Tools}{Git, Docker, Railway, CI/CD, Linux}

\end{document}